Quick, Draw! Image Classification

### 2018-12-08 report/draft.tex
draft ready for review, let me know if the grammar is atrocious

@@

Results can be seen in the Appendix with Figure \ref{fig:h4Results}. 
We get unexpectedly high accuracy of 43\% even in the worst case of 1:500
imbalance in the categories while attempting to classify only the minority
categories. This is because neural networks tend to generalize well on the
most important weights.

@@

Talk about our final slide and tie the hypotheses together

@@

@@

\begin{figure}[h!]
  \begin{center}
    \includegraphics[scale=0.5]{fig8}
    \end{center}
  \caption{$H3_a$ Results for various size training data}
  \label{fig:h3Results}
  \end{figure}

>>>>

\subsection{Baseline image classification using humans}

Our baseline performance when manually classifying images into one
of 10 categories is 87\% accuracy on average. We consider this accuracy to
be ``reasonable accuracy''. The accuracy serves as a baseline for informing
our understanding of results for our models.

@@

Results can be seen in the Appendix with Figure \ref{fig:h4Results}.
Increasing the number of categories will cause a significant drop in the
performance of the neural network. Increasing the overall data points for
the network to be trained on should help.

We try and understand the limits and capacity of the finalized model by
varying the number of categories and the number of rows per category. We
then measure the response accuracy and response loss of the model. The
number of rows per category is altered in steps of 1000 from 7,000 to 20,000
and the number of categories is altered in steps of 1 from 3 to 10.

3 examples of the accuracy measurements with most rows (14,000), least rows
(2,000) and intermediate rows (7,000) and their performance per every
additional category is plotted below.

@@

Our hypotheses explored how modeling choices and data distribution affect
the accuracy performance. We found convolutional neural networks to be a
good approach for classifying spatial data like images. Convolutional neural
networks gave a better accuracy than humans which in turn was better than
accuracy by fully connected neural networks.

In terms of modeling choices, Fully connected neural network(FC-NN)
performed reasonably well for the Quick Draw dataset classification. We
noted that Convolutional Neural network’s(CNN) training and testing accuracy
was 5 percent better than the FC-NN. Additionally,  CNN was 13 times faster
to train than FC-NN. These results highlighted the optimizations done by
CNN with local connectivity and parameter sharing. The change in accuracy
and speed is likely to be amplified as we scale the model up with respect
to model complexity or data.

In terms of data distribution, we noted that for every additional category
added to the finalized model architecture resulted in a 1.88\% decrease in
test accuracy. Training the model on an imbalanced distribution of classes
resulted in a poor prediction accuracy for the minority class. The
prediction accuracy for the minority class increased as the imbalance in
the training dataset decreased.

In the future, we would like to make use of the time-series data for the
drawings to predict the object while it is being drawn.

@@

Our project code is available in a GitHub repo: ``https://github.com/tbonza/ds5220''.

@@

\begin{figure}[h!]
  \begin{center}
    \includegraphics[scale=0.5]{fig8}
    \end{center}
  \caption{$H3_a$ Results for various size training data at (epoch 1,
    epoch 10)}
  \label{fig:h3Results}
  \end{figure}
